### 2023-09-22 sections/working-papers.tex
Update working-papers.tex

\begin{benumerate}{3}

\item{\small González-Bustamante, B., \& Aguilar, D. (2022). Data Set on Local Government Indicators in Chile (Version 0.20.14 -- Late Butterfly) [Data set]. Pre-release version under restricted access. {\scshape doi:} \href{https://doi.org/10.5281/zenodo.6848053}{\textcolor{blue}{10.5281/zenodo.6848053}}.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Olivares, A. (2022). Data Set on Chilean Ministers (1990-2014) (Version 3.3.6 -- Dry Bonus) [Data set]. {\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}.}\vspace{1mm}

\item{González-Bustamante, B., \& Olivares, A. (2022). Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.3 -- Shiny Snow) [Data set]. {\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}

@@

\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A. (2016). Revolving Door. Analysis of Public-Private Circulation in Chile (2000-2014). {\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, 7, 1--40. {\footnotesize \scshape [in Spanish]}. {\scshape doi:} \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Olivares, A. (2016). Undersecretaries Rotation in the Chilean Cabinets (1990-2014). {\itshape Observat\'orio de elites pol\'iticas e sociais do Brasil. NUSP/UFPR, 3}(5), 1--19. {\footnotesize \scshape [in Portuguese]}. {\scshape url:} \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Soto, D. (2016). Pluralism in the Chilean Digital Mass Media, Exploratory Study of Key Cases. {\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, 2, 1--26. {\footnotesize \scshape [in Spanish]}. {\scshape doi:} \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}.}\vspace{1mm}

\item{\small González-Bustamante, B. (2015). Programas de Naciones Unidas para el Desarrollo (PNUD). (2014). Ciudadanía Política: Voz y Participación Ciudadana en América Latina. Buenos Aires: Siglo Veintiuno Editores. {\itshape Revista de Gestión Pública, IV}(1), 143--149. {\footnotesize \scshape [in Spanish]}. {\scshape doi:} \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}.}\vspace{1mm}

>>>>

\begin{benumerate}{6}

\item{\small González-Bustamante, B., \& Aguilar, D. (2023). Data Set on Local Government Indicators in Chile (Version 0.20.15 -- Late Sky). Dataset, pre-release version, University of Oxford, Universidad de Santiago de Chile (USACH) and Training Data Lab. {\scshape doi:} \href{https://doi.org/10.5281/zenodo.6848053}{\textcolor{blue}{10.5281/zenodo.6848053}}.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Olivares, A. (2023). Data Set on Chilean Ministers (1990-2014) (Version 3.3.7 -- Soft Dew). Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor and Training Data Lab. {\scshape doi:} \href{https://doi.org/10.5281/zenodo.5744536}{\textcolor{blue}{10.5281/zenodo.5744536}}.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Olivares, A. (2023). Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.4 -- Wandering Grass). Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor and Training Data Lab. {\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Olivares, A. (2023). Data Set on Chilean Undersecretaries (1990-2022) (Version 2.1.4 -- Wandering Grass). Dataset, University of Oxford, Universidad de Santiago de Chile (USACH), Universidad Mayor and Training Data Lab. {\scshape doi:} \href{https://doi.org/10.5281/zenodo.5715384}{\textcolor{blue}{10.5281/zenodo.5715384}}.}\vspace{1mm}

\item{\small González-Bustamante, B. et al. (2023). Chilean Political Science Ranking. Dataset, University of Oxford, Universidad de Santiago de Chile (USACH) and Training Data Lab. {\scshape doi:} \href{http://doi.org/10.17605/OSF.IO/C8PRA}{\textcolor{blue}{10.17605/OSF.IO/C8PRA}}.}\vspace{1mm}

\item{\small González-Bustamante, B. et al. (2021). Survival of the Senior Civil Servants in the Chilean Executive Branch (Version 1.13.19 -- Bold Lab). Dataset, pre-release version under restricted access, University of Oxford, Universidad de Santiago de Chile (USACH) and Training Data Lab. {\scshape doi:} \href{https://doi.org/10.5281/zenodo.8115596}{\textcolor{blue}{10.5281/zenodo.8115596}}.}\vspace{1mm}

@@

%% \item{\small Maillet, A., González-Bustamante, B., \& Olivares, A. (2016). Revolving Door. Analysis of Public-Private Circulation in Chile (2000-2014). {\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, 7, 1--40. {\footnotesize \scshape [in Spanish]}. {\scshape doi:} \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}.}\vspace{1mm}

\item{\small Maillet, A., González-Bustamante, B., \& Olivares, A. (2016). ¿Puerta giratoria? Análisis de la circulación público-privada en Chile (2000-2014). {\itshape Serie Documentos de Trabajo PNUD-Desigualdad}, 7, 1--40. {\scshape doi:} \\ \href{http://doi.org/10.13140/RG.2.2.25510.42566}{\textcolor{blue}{10.13140/RG.2.2.25510.42566}}.}\vspace{1mm}

%% \item{\small González-Bustamante, B., \& Olivares, A. (2016). Undersecretaries Rotation in the Chilean Cabinets (1990-2014). {\itshape Newsletter. Observat\'orio de elites pol\'iticas e sociais do Brasil. NUSP/UFPR, 3}(5), 1--19. {\footnotesize \scshape [in Portuguese]}. {\scshape url:} \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Olivares, A. (2016). A rotatividade de subsecretários dos ministérios no Chile (1990-2014). {\itshape Newsletter. Observat\'orio de elites pol\'iticas e sociais do Brasil. NUSP/UFPR, 3}(5), 1--19. {\scshape url:} \\ \href{https://www.researchgate.net/publication/321993740_A_rotatividade_de_subsecretarios_dos_ministerios_no_Chile_1990-2014}{\textcolor{blue}{www.researchgate.net}}.}\vspace{1mm}

%% \item{\small González-Bustamante, B., \& Soto, D. (2016). Pluralism in the Chilean Digital Mass Media, Exploratory Study of Key Cases. {\itshape Serie Pol\'itica, Gesti\'on y Pol\'iticas P\'ublicas}, 2, 1--26. {\footnotesize \scshape [in Spanish]}. {\scshape doi:} \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}.}\vspace{1mm}

\item{\small González-Bustamante, B., \& Soto, D. (2016). Pluralismo en los medios digitales escritos en Chile, una exploración de casos clave. {\itshape Serie Política, Gestión y Políticas Públicas}, 2, 1--26. {\scshape doi:} \href{http://doi.org/10.13140/RG.2.2.33899.03362/1}{\textcolor{blue}{10.13140/RG.2.2.33899.03362/1}}.}\vspace{1mm}

%% \item{\small González-Bustamante, B. (2015). Programas de Naciones Unidas para el Desarrollo (PNUD). (2014). Ciudadanía Política: Voz y Participación Ciudadana en América Latina. Buenos Aires: Siglo Veintiuno Editores. {\itshape Revista de Gestión Pública, IV}(1), 143--149. {\footnotesize \scshape [in Spanish]}. {\scshape doi:} \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}.}\vspace{1mm}

\item{\small González-Bustamante, B. (2015). Programas de Naciones Unidas para el Desarrollo (PNUD). (2014). Ciudadanía Política: Voz y Participación Ciudadana en América Latina. Buenos Aires: Siglo Veintiuno Editores. {\itshape Revista de Gestión Pública, IV}(1), 143--149. {\scshape doi:} \href{https://doi.org/10.22370/rgp.2015.4.1.2240}{\textcolor{blue}{10.22370/rgp.2015.4.1.2240}}.}
